Winter 2025 ToDo

### 2025-12-04 Relations/Paper/Well-foundedness.tex
Fixed minor macro issues

An abstract reduction $\to_R$ is strongly normalizing
if and only if the converse relation is well-founded.
In this section, we will compare several definitions of well-foundedness.
For ease of exposition, we will only consider local versions of these notions.
(There is no loss of generality in this; any global well-foundedness property $\gWF(A;R)$ 
restricts to a predicate $WF_R$ on $A$ via $WF_R(x) = \gWF(\Sigma y : A. R^* x y;R')$, 
where $R'((y,\rho),(z,\sigma)) = R(y,z)$.)
%which depend on the basic notions given in Definition~\ref{def:WFnotions} below.

@@

\begin{definition} \label{def:WFproperties} \hfill
  \begin{enumerate}
    \item $R$ is \emph{accessibly well-founded} ($\WFacc$) if every element is accessible:
      \[
        \forall x \in A.\; x \text{ is accessible}
      \]
    \item \label{def:WFind} $R$ is \emph{inductively well-founded} ($\WFind$) if every inductive predicate is universally true:
      \[
        \forall P \subseteq A.\;\text{$P$ is inductive} \Rightarrow \forall x \in A.\; x \in P
      \]
    \item $R$ is \emph{coreductively well-founded} ($\WFcor$) if every coreductive predicate is universally true:
      \[
        \forall P \subseteq A.\;\text{$P$ is coreductive} \Rightarrow \forall x \in A.\; x \in P
      \]
    \item  $R$ is \emph{well-founded minimality-wise} ($\WFmin$) if every nonempty subset contains a minimal element:
      \[
        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow
        \exists x \in A.\; \text{$x$ is $P$-minimal}
      \]
    \item  $R$ is \emph{well-founded minimality-wise for $\lnot \lnot$-closed predicates} ($\WFminDNE$) if every nonempty $\lnot \lnot$-closed subset contains a minimal element:
      \[
        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \ol{\ol P} \subseteq P \Rightarrow
        \exists x \in A.\; \text{$x$ is $P$-minimal}
      \]
   \item $R$ is \emph{sequentially well-founded} ($\WFseq$) if every sequence contains an index at which it is not decreasing:
      \[
        \forall s : \nat \to A\ \exists k : \nat.\, \lnot \, R \,(s\,(k+1))\,(s\,k)
      \]
  \end{enumerate}
\end{definition}
We have formalized the above definitions of well-foundedness in \texttt{WFDefinitions.agda}.

@@

\begin{definition} \label{def:WFweakproperties} \hfill
  \begin{enumerate}
    \item $R$ is \emph{weakly accessibly well-founded} ($\WFaccm$) if accessibility holds for all elements up to double negation:
      \[
        \forall x \in A.\; \lnot \lnot  (x \text{ is accessible})
      \]
    \item $R$ is \emph{weakly inductively well-founded} ($\WFindm$) if every inductive predicate holds for all elements up to double negation:
      \[
        \forall P \subseteq A.\;\text{$P$ is inductive} \Rightarrow \forall x \in A.\; \lnot \lnot (x \in P)
      \]
    \item $R$ is \emph{weakly coreductively well-founded} ($\WFcorm$) if every coreductive predicate holds for all elements up to double negation:
      \[
        \forall P \subseteq A.\;\text{$P$ is coreductive} \Rightarrow \forall x \in A.\; \lnot\lnot(x \in P)
      \]
    \item  $R$ is \emph{weakly well-founded minimality-wise} ($\WFminm$)
      if for every nonempty subset $P$ there $\lnot \lnot$-exists a minimal element in $P$:
      \[
        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \lnot \lnot \;
        (\exists x \in A.\; \text{$x$ is $P$-minimal})
      \]
    \item  $R$ is \emph{weakly well-founded minimality-wise for $\lnot \lnot$-closed predicates} ($\WFminDNEm$)
      if for every nonempty $\lnot \lnot$-closed subset $P$ there $\lnot \lnot$-exists a minimal element in $P$:
      % \[
      %   \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \left(\ol{\ol P} \subseteq P\right) \Rightarrow \lnot \lnot \;
      % (\exists x \in P.\; \text{$x$ is $P$-minimal}) \]
      \[
        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \ol{\ol P} \subseteq P\Rightarrow \lnot \lnot \;
        (\exists x \in A.\; \text{$x$ is $P$-minimal})
      \]
  \item $R$ is \emph{weakly sequentially well-founded} ($\WFseqm$) if no sequence is $R$-decreasing:
    \[
      \forall s:\nat \to A.\; \lnot \text{($s$ is $R$-decreasing)}
    \]
\end{enumerate}
\end{definition}

@@

The logical relationships between all of the above definitions are summarized in Figure~\ref{fig:WF}.
All of the implications in the figure have been
formalized within the WellFounded subdirectory of the Agda repository.
An arrow from one node to another with no label indicates direct logical implication,
provable constructively with no additional assumptions. An arrow with a label indicates an additional
(semi-)classical hypothesis needed to establish the implication.
The definitions of these hypotheses are given in Figure \ref{tab:cprop}.

We consider $\WFacc$ to be the canonical constructive definition of
a well-founded relation (hence the emphasis in the figure).
In the ARS setting, this corresponds to defining
strong normalization inductively in terms of reductions to normal forms.
As can be seen from the figure, it is implied by
Terese's definition $\WFseqm$ only when \emph{two}
strongly classical conditions are in place.
These are $\accDNE$ (not-not-closure of strong normalization)
and $\accCor$ (which is related to the existence of an effective perpetual reduction strategy).

@@

{
\def\arraystretch{1.3}
\begin{figure}[h!]
\small
\begin{tabular}{@{}l l l @{}}
\toprule
\textbf{Property} & \textbf{Definition}  &\textbf{Agda Code}  \\
\midrule
$\rdec$   & $R$ is decidable
          & $\forall$ \verb|{x} {y}| $\to$ \verb|EM (R x y)|\\
$\FB$     & $R$ is finitely branching
          & $\mathtt{\forall (a : A) \to \Sigma [ xs \in List A ] (\forall b \to R a b \to b \in{}List\, xs)}$ \\
$\mpe$    & Sequences are $\lnot\lnot$-closed
          & $\forall\ \mathtt{(f : \nat \to A) \to \lnot\lnot Closed
          (\lambda x \to \Sigma [ k \in \nat ] (f\, k \equiv x))}$ \\
$\corDNE$ & Coreductives are $\lnot\lnot$-closed
          & $\mathtt{\forall (P : \mathcal{P} A) \to R}$-$\mathtt{coreductive\ P \to \lnot\lnot Closed\ P}$\\
$\accDNE$ & Accessibility is $\lnot\lnot$-closed
          & $\lnot\lnot$\verb|Closed (R -accessible)| \\
$\accCor$ & Accessibility is coreductive
          & \verb|R -coreductive (R -accessible)| \\
\bottomrule
\end{tabular}
\centering
\caption{Classical Properties Used in the Well-Foundedness Diagram}
\label{tab:cprop}
\end{figure}
}
% \clearpage
% The principles appearing in the labels of Figure \ref{fig:WF} are valid for many rewriting systems,
% and are classically true.
Figure \ref{fig:WF} illustrates that the network of logical relationships between
constructive notions of well-foundedness is quite rich indeed.
Taking the $\lnot\lnot$-closures of
these notions cuts down some, but not all, of the complexity.
For example, the two minimality principles become equivalent.
% The implication from the inductive to sequential definition no longer requires
% decidability of $R$.
% On the other hand, the reverse
At the same time, the weak version of the sequential definition is unable to imply
the (weak) accessible one without an additional hypothesis $\accCor$,
which may be described as the constructive contrapositive of the definition of accessibility.
In the context of rewriting systems,
this condition asserts the existence of a function which maps any
element that is \emph{not} strongly normalizing to a one-step reduct of it having the same property.
Assuming $\accCor$, all notions of well-foundedness
are constructively equivalent up to $\lnot\lnot$.

@@

We have also considered the statement that the complement of every coreductive predicate
  has a least element.  This statement and its $\lnot\lnot$-version are both equivalent to $\WFcorm$
  (see \texttt{CoreductiveImplications.agda}), so we have not included them in the figure.

We also did not include the inductive definition, Definition \ref{def:WFproperties}.\ref{def:WFind}.
  Logically, it is trivially equivalent to the accessible one, but its Agda formalization has a defect:
  the inductive well-foundedness property lands in the larger universe $\mathtt{Set}_1$, due to
  quantification over all predicates on $A$.  This defect is also present in $\WFmin$, $\WFminDNE$,
  and $\WFcor$.

@@

Such distinctions have consequences for rewriting theory.
For example, recall that $x\in \SN_R$ iff $x$ is $\bar{R}$-accessible, where $\bar{R}$
is the converse of $R$.  Thus, if $\bar{R}$ is well-founded, $R \models \gSN$.
Yet actually computing the normal form of a given $x$ requires a
strong form of decidability of being $R$-minimal:
\[
\tag{$\isMinDec$} \forall x. \left(\exists y. Ryx\right) \lor \left(\forall y. \lnot Ryx\right)
\]
Note that merely deciding whether $x$ is a normal form is the weaker statement
% Note that deciding whether $x$ is a normal form constitutes the weaker disjunction
$\lnot\lnot\left(\exists y. Ryx\right) \lor \left(\forall y. \lnot Ryx\right)$.
Indeed, in the file \texttt{ARS/Examples.agda} the implication $\gSN \to \gWN$ for all relations $R$
is shown to be equivalent to the principle of excluded middle.

>>>>

An abstract reduction $\to_R$ is strongly normalizing
if and only if the converse relation is well-founded.
In this section, we will compare several definitions of well-foundedness.
For ease of exposition, we will only consider global versions of these notions.
(There is no loss of generality in this; any global well-foundedness property $\gWF(A;R)$ 
restricts to a predicate $WF_R$ on $A$ via $WF_R(x) = \gWF(\Sigma y {:} A. R^* x y;R')$, 
where $R'((y,\rho),(z,\sigma)) = R(y,z)$; now $\gWF(A;R) \leftrightarrow \forall x. WF_R(x)$.)
%which depend on the basic notions given in Definition~\ref{def:WFnotions} below.

@@

\begin{definition} \label{def:WFproperties} \hfill
  \begin{itemize}
    \item $R$ is \emph{accessibly well-founded} ($\WFacc$) if every element is accessible:
      \[
        \forall x \in A.\; x \text{ is accessible}
      \]
    \item %\label{def:WFind}
      $R$ is \emph{inductively well-founded} ($\WFind$) if every inductive predicate is universally true:
      \[
        \forall P \subseteq A.\;\text{$P$ is inductive} \Rightarrow \forall x \in A.\; x \in P
      \]
    \item $R$ is \emph{coreductively well-founded} ($\WFcor$) if every coreductive predicate is universally true:
      \[
        \forall P \subseteq A.\;\text{$P$ is coreductive} \Rightarrow \forall x \in A.\; x \in P
      \]
    \item  $R$ is \emph{well-founded minimality-wise} ($\WFmin$) if every nonempty subset contains a minimal element:
      \[
        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow
        \exists x \in A.\; \text{$x$ is $P$-minimal}
      \]
    \item  $R$ is \emph{well-founded minimality-wise for $\lnot \lnot$-closed predicates} ($\WFminDNE$) if every nonempty $\lnot \lnot$-closed subset contains a minimal element:
      \[
        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \ol{\ol P} \subseteq P \Rightarrow
        \exists x \in A.\; \text{$x$ is $P$-minimal}
      \]
   \item $R$ is \emph{sequentially well-founded} ($\WFseq$) if every sequence contains an index at which it is not decreasing:
      \[
        \forall s : \nat \to A\ \exists k : \nat.\, \lnot \, R \,(s\,(k+1))\,(s\,k)
      \]
  \end{itemize}
\end{definition}
We have formalized the above definitions of well-foundedness in \texttt{WFDefinitions.agda}.

@@

\begin{definition} \label{def:WFweakproperties} \hfill
  \begin{itemize}
    \item $R$ is \emph{weakly accessibly well-founded} ($\WFaccm$) if accessibility holds for all elements up to double negation:
      \[
        \forall x \in A.\; \lnot \lnot  (x \text{ is accessible})
      \]
    \item $R$ is \emph{weakly inductively well-founded} ($\WFindm$) if every inductive predicate holds for all elements up to double negation:
      \[
        \forall P \subseteq A.\;\text{$P$ is inductive} \Rightarrow \forall x \in A.\; \lnot \lnot (x \in P)
      \]
    \item $R$ is \emph{weakly coreductively well-founded} ($\WFcorm$) if every coreductive predicate holds for all elements up to double negation:
      \[
        \forall P \subseteq A.\;\text{$P$ is coreductive} \Rightarrow \forall x \in A.\; \lnot\lnot(x \in P)
      \]
    \item  $R$ is \emph{weakly well-founded minimality-wise} ($\WFminm$)
      if for every nonempty subset $P$ there $\lnot \lnot$-exists a minimal element in $P$:
      \[
        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \lnot \lnot \;
        (\exists x \in A.\; \text{$x$ is $P$-minimal})
      \]
    \item  $R$ is \emph{weakly well-founded minimality-wise for $\lnot \lnot$-closed predicates} ($\WFminDNEm$)
      if for every nonempty $\lnot \lnot$-closed subset $P$ there $\lnot \lnot$-exists a minimal element in $P$:
      % \[
      %   \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \left(\ol{\ol P} \subseteq P\right) \Rightarrow \lnot \lnot \;
      % (\exists x \in P.\; \text{$x$ is $P$-minimal}) \]
      \[
        \forall P \subseteq A.\; P \neq \varnothing \Rightarrow \ol{\ol P} \subseteq P\Rightarrow \lnot \lnot \;
        (\exists x \in A.\; \text{$x$ is $P$-minimal})
      \]
  \item $R$ is \emph{weakly sequentially well-founded} ($\WFseqm$) if no sequence is $R$-decreasing:
    \[
      \forall s:\nat \to A.\; \lnot \text{($s$ is $R$-decreasing)}
    \]
\end{itemize}
\end{definition}

@@

The logical relationships between all of the above definitions are summarized in Figure~\ref{fig:WF}.
All of the implications in the figure have been
formalized within the \texttt{WellFounded} subdirectory of the Agda repository.
An arrow from one node to another with no label indicates direct logical implication,
provable constructively with no additional assumptions. An arrow with a label indicates an additional
(semi-)classical hypothesis needed to establish the implication.
The definitions of these hypotheses are given in Figure \ref{tab:cprop}.

We consider $\WFacc$ to be the canonical constructive definition of
a well-founded relation (hence the emphasis in the figure).
In the ARS setting, this corresponds to defining
strong normalization inductively in terms of reductions to normal forms.
As can be seen from the figure, it is implied by
$\WFseqm$ (the definition used by \terese) only when \emph{two}
strongly classical conditions are in place.
These are $\accDNE$ (not-not-closure of strong normalization)
and $\accCor$ (which is related to the existence of an effective perpetual reduction strategy).

@@

{
\def\arraystretch{1.3}
\begin{figure}[h!]
\small
% \renewcommand{\Sigma}{{\scriptstyle{\sum}}}
% \renewcommand{\Sigma}{{\sum}}
\begin{tabular}{@{}l l l @{}}
\toprule
\textbf{Property} & \textbf{Definition}  &\textbf{Agda Code}  \\
\midrule
$\rdec$   & $R$ is decidable
          & $\forall$ \verb|{x} {y}| $\to$ \verb|EM (R x y)|\\
$\FB$     & $R$ is finitely branching
          & $\mathtt{\forall (a : A) \to}\Sigma\mathtt{[ xs \in List A ] (\forall b \to R a b \to b \in{}List\, xs)}$ \\
$\mpe$    & Sequences are $\lnot\lnot$-closed
          & $\forall\ \mathtt{(f : \nat \to A) \to \lnot\lnot Closed
        (\lambda x \to} \Sigma \mathtt{[ k \in \nat ] (f\, k \equiv x))}$ \\
$\corDNE$ & Coreductives are $\lnot\lnot$-closed
          & $\mathtt{\forall (P : \mathcal{P} A) \to R}$-$\mathtt{coreductive\ P \to \lnot\lnot Closed\ P}$\\
$\accDNE$ & Accessibility is $\lnot\lnot$-closed
          & $\lnot\lnot$\verb|Closed (R -accessible)| \\
$\accCor$ & Accessibility is coreductive
          & \verb|R -coreductive (R -accessible)| \\
\bottomrule
\end{tabular}
\centering
\caption{Classical Properties Used in the Well-Foundedness Diagram}
\label{tab:cprop}
\end{figure}
}
% \clearpage
% The principles appearing in the labels of Figure \ref{fig:WF} are valid for many rewriting systems,
% and are classically true.
Figure \ref{fig:WF} illustrates that the network of logical relationships between
constructive notions of well-foundedness is quite rich indeed.
Taking the $\lnot\lnot$-closures of
these notions cuts down some, but not all, of the complexity.
For example, the two minimality principles become equivalent.
% The implication from the inductive to sequential definition no longer requires
% decidability of $R$.
% On the other hand, the reverse
At the same time, the implication from the weak version of the sequential definition 
to the (weak) accessible one still requires the hypothesis $\accCor$,
which may be described as the constructive contrapositive of the definition of accessibility.
In the context of rewriting systems,
this condition asserts the existence of a function which maps any
element that is \emph{not} strongly normalizing to a one-step reduct of it having the same property.
Assuming $\accCor$, all notions of well-foundedness
are constructively equivalent up to $\lnot\lnot$.

@@

We have also considered the statement that the complement of every coreductive predicate
  has a least element.  This statement and its $\lnot\lnot$-version are both equivalent to $\WFcorm$
  (see \texttt{WFCoreductiveImplications.agda}), so we have not included them in the figure.

We also did not include $\WFind$ from Definition \ref{def:WFproperties}.
Logically, it is trivially equivalent to the accessible one, but its Agda formalization has a defect:
  the inductive well-foundedness property lands in the larger universe $\mathtt{Set}_1$, due to
  quantification over all predicates on $A$.  This defect is also present in $\WFmin$, $\WFminDNE$,
  and $\WFcor$.

@@

Such distinctions have consequences for rewriting theory.
For example, recall that $x\in \SN_R$ iff $x$ is $\tilde{R}$-accessible, where $\tilde{R}$
is the converse of $R$.  Thus, if $\tilde{R}$ is well-founded, $R \models \gSN$.
Yet actually computing the normal form of a given $x$ requires a
strong form of decidability of being $R$-minimal:
\[
  \tag{$\isMinDec$} \forall x. \left(\exists y. x \rstep y \right) \lor \left(\forall y. x \nrstep y\right)
\]
Note that merely deciding whether $x$ is a normal form is the weaker statement
% Note that deciding whether $x$ is a normal form constitutes the weaker disjunction
$\lnot\lnot\left(\exists y. x \rstep y\right) \lor \left(\forall y. x \,\,\not \!\!\!\! \rstep y\right)$.
Indeed, in the file \texttt{ARS/Examples.agda} the implication $\gSN \to \gWN$ for all relations $R$
is shown to be equivalent to the principle of excluded middle.

### 2025-12-04 Relations/Paper/Winter_2025_TODO.tex
Fixed minor macro issues

\section*{December 2025}
\subsection*{Carry over from previous TODO}
\begin{todolist}
    \item (Review 3) * From the formalization, the authors could explain some features and syntax of Agda for readers unfamiliar with this proof assistant. What were the main attributes of Agda that helped you in the formalization process? In line 204, the paper brings the definition of an element being finitely branching and states that the formulation of such a definition is given in line 206. FB a seems to be a set (in line 206), not a boolean. Also, in the formalization of FB a, the authors use R b a instead of R a b. What elements of Agda allow such specification capturing exactly Def. 12.
    \item  Create an equivalences file showing that our formalization agrees with the ASL (specifically definitions such as confluent, wcr, nf, leading up to showing our formalizations of Newman's lemma agree).
  \item Investigate contributing work to the ASL. This may mean refactoring the work already done to conform with the ASL. Specific contributions would likely be: Generalized NL. Theorem's 122 and 123. Alternative definitions of Well-founded, the implications for the hierarchy.
  \item  It's possible to have a term rewrite system with good properties like FB and the relation being decidable. But not satisfying accCor. That is something that can be added in a final touch of the paper. Either a remark or example, where a term rewrite system does not validate accCor. (In the lambda calculus, there are computable perpetual strategies. We think they're concerned with weak normalization. Not sure if it can be done with strong normalization.)
  \item Is there a path from WFseq- with MP== to WFseq? (W're thinking it will need rdec as well to give us the implication
  ).
 \item incorporate wfseq not not to the paper?
 \item We want to start looking at examples. What we want to know is whether a first order rewrite system with some minimal properties implies some of our classical properties. E.g. lambda calculus satisfies some of our classical properties. As does first order term rewrite system. Follow up question: how big of an issue is it that accCor is not provable? Can we prove is isn't satisfied? 
 \item check TERESE and see first order term rewrite systems example which could be valid for showing classical and constructive formalization coincide. First order term rewrite systems are (always?) fb and R is dec. 
  \item Make the well founded definitions conform to the style of the definitions in other sections. Namely, bring the symbols to the start of the sentence. Use bemph where appropriate. Do we want all definitions to be itemized?
  \item Improve how we write P bar bar for the definitions in wellfounded (well founded minimality wise). Chat makes the following suggestion (see commented out line in tex file):
  % \newcommand{\dneg}[1]{\overline{\smash{\overline{#1}}\vphantom{#1}}} % tight double overline
  \item The sigma symbol was being rendered as a degree symbol. Why? Also, our solution is slightly too big, try and make it smaller (see well founded classical definitions).
  \item We made a bodge fix for not right arrow in use in well founded. It is good enough for now but there should be a better way to express it in latex. (when defining isMinDec)
  \item Go through the code, make naming consistent and self-documenting
  \item run through the table again and check the counterexamples line up. 
  \item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code). Similarly it should be the double arrow iff. Check through paper for similar changes.

>>>>

\section*{December 2025}
\subsection*{Carry over from previous TODO}
\begin{todolist}
    \item (Review 3) * From the formalization, the authors could explain some features and syntax of Agda for readers unfamiliar with this proof assistant. What were the main attributes of Agda that helped you in the formalization process? In line 204, the paper brings the definition of an element being finitely branching and states that the formulation of such a definition is given in line 206. FB a seems to be a set (in line 206), not a boolean. Also, in the formalization of FB a, the authors use R b a instead of R a b. What elements of Agda allow such specification capturing exactly Def. 12.
    \item  Create an equivalences file showing that our formalization agrees with the ASL (specifically definitions such as confluent, wcr, nf, leading up to showing our formalizations of Newman's lemma agree).
  \item Investigate contributing work to the ASL. This may mean refactoring the work already done to conform with the ASL. Specific contributions would likely be: Generalized NL. Theorem's 122 and 123. Alternative definitions of Well-founded, the implications for the hierarchy.
  \item  It's possible to have a term rewrite system with good properties like FB and the relation being decidable. But not satisfying accCor. That is something that can be added in a final touch of the paper. Either a remark or example, where a term rewrite system does not validate accCor. (In the lambda calculus, there are computable perpetual strategies. We think they're concerned with weak normalization. Not sure if it can be done with strong normalization.)
  \item Is there a path from WFseq- with MP== to WFseq? (W're thinking it will need rdec as well to give us the implication
  ).
 \item incorporate wfseq not not to the paper?
 \item We want to start looking at examples. What we want to know is whether a first order rewrite system with some minimal properties implies some of our classical properties. E.g. lambda calculus satisfies some of our classical properties. As does first order term rewrite system. Follow up question: how big of an issue is it that accCor is not provable? Can we prove is isn't satisfied? 
 \item check TERESE and see first order term rewrite systems example which could be valid for showing classical and constructive formalization coincide. First order term rewrite systems are (always?) fb and R is dec. 
  \item Make the well founded definitions conform to the style of the definitions in other sections. Namely, bring the symbols to the start of the sentence. Use bemph where appropriate. Do we want all definitions to be itemized?
  \item Improve how we write P bar bar for the definitions in wellfounded (well founded minimality wise). Chat makes the following suggestion (see commented out line in tex file):
  % \newcommand{\dneg}[1]{\overline{\smash{\overline{#1}}\vphantom{#1}}} % tight double overline
  (Have tried a number of solutions, none seem to quite get what we want. Putting this off for now as low priority.)
  \item The sigma symbol was being rendered as a degree symbol. Why? Also, our solution is slightly too big, try and make it smaller (see well founded classical definitions).
  \item [\done] We made a bodge fix for not right arrow in use in well founded. It is good enough for now but there should be a better way to express it in latex. (when defining isMinDec) (new macro nrstep fixes it). 
  \item Go through the code, make naming consistent and self-documenting
  \item run through the table again and check the counterexamples line up. 
  \item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code). Similarly it should be the double arrow iff. Check through paper for similar changes.
